A continuous urbanization index to assess phylogenetic adaptations in urban bird living

### 2018-05-17 ms.Rmd
looking better... try remaking now...

### Phylogenetic signal
There was a distinct phylogenetic signal in our urbanization index measure (Fig. 3; Table 1), as it was significantly different than random for 4 out of the 5 indices considered. Additionally, there was strong phylogenetic signal for potential predictor traits, especially body size and brain residual (Table 1). The result for body size ($k=3.3$) is among the strongest ever recorded measures of phylogenetic signal in the literature, and for $k$ the statistic suggests much stronger signal than expected from Brownian motion. We generally found weaker signal for behavioral traits compared with morphological traits. For these traits, the estimates of phylogenetic signal were weaker than Brownian motion but significant in most cases (Table 1).

@@

# DISCUSSION
Niche breadth, as measured by different types of generalism, was significantly associated with urbanization in our analyses, evidenced by the robustness of this result across non-phylogenetic and phylogenetic models, model-averaging approaches, and across phylogenetic uncertainty (Fig. S2). Conversely, specialized feeding strategies were negatively associated with urbanization: granivorous and insectivorous specialists were much less likely to be found in urban environments. These results suggest that urbanization is, in general, excluding specialist species [@sorace2009distribution]. As such, future urban development aimed at increasing avian diversity in urban areas should focus on maintaining a high diversity of habitat [@melles2003urban] both for foraging [@shochat2004linking], and nesting [@fernandez2001habitat], with a focus on intact vegetation [@sushinsky2013should] connected by corridors [@litteral2017role]. A species-specific approach to assess particular resources necessary for specialist species may be necessary [@fernandez2004spatial]. Furthermore, a focal point of avian biodiversity conservation should be on increasing insect abundance and diversity in urban environments [@baldock2015uk], which will in turn benefit avian biodiversity in urban environments.

The non-random distribution of the urbanization index across the phylogeny (Table 1) is consistent with the observation of reduced phylogenetic diversity in urban areas [@la2018phylogenetic], suggesting that there are phylogenetic constraints which allow certain birds to persist within urban environments [@morelli2016evidence; @ibanez2017global; @sol2017urbanisation]. This finding of a strong phylogenetic signal contrasts with previous studies [@evans2011makes], but this is likely a result of increased statistical power from our larger sample size: 477 species in this study compared with 55 species in Evans *et al.* [-@evans2011makes]. It's not surprising that a larger sample size finds a non-random pattern in urbanization across the bird phylogeny and we demonstrated the importance of treating species as non-independent by considering phylogeny in the context of the linear models. For example, some predictor variables became less crucial in the phylogenetically controlled models compared with the non-phylogenetic models, including some feeding types (i.e., insect specialists) and habitat preferences (i.e., agricultural). For these variables, it is likely that there may be particular clades which include a number of species that are associated with both that particular trait and urbanization [see @felsenstein1985confidence]. Conversely, some of the most important predictor variables (e.g., clutch size and feeding habitat generalism; Figures 4 and 5) showed a stronger relationship (i.e., increased parameter estimates) with urbanization when phylogeny was accounted for, and this affect was robust relative to a consideration of phylogenetic uncertainty (Fig. S2). Furthermore, residual brain mass (and body size to a lesser extent) was significantly important within the phylogenetic models, but not in the non-phylogenetic models, suggesting that within a clade the species with the largest residual brain mass [@maklakov2011brains] and largest body size [@major2010museum] are most suited to surviving in urban areas. While some studies have found a lack of evidence that residual brain size is an important predictor in urban birds [@kark2007living; @evans2011makes], our results suggest that residual brain size is indeed heavily correlated with urbanization in birds [@moller2009successful; @maklakov2011brains; @moller2015brain]. This finding highlights the necessity to investigate the trait-urbanization relationships in a phylogenetically informed manner.

Certian aspects of the trait-urbanization relationship appear to be consistent, and thus generalizable, across the globe. For instance, our finding of the relative importance of annual fecundity is consistent with work in Europe [@croci2008does; @moller2009successful]. Urbanization appears to generally select against insectivorous species [@chace2006urban; @evans2011makes]. Although we did not find any strong support for our hypotheses on different nesting types, we did find that in general species which tended to be more social were closely associated with urbanization, consistent with other findings [@coleman1994neophobia; @jokimaki1998distribution; @kark2007living]. While these patterns may be generalizable, we also found patterns in our analysis which seem to contrast the global norm. For example, we found that urbanization selects against granivorous species, contrasting the general trend [@chace2006urban; @kark2007living; @evans2011makes], but this could be a result of relatively little supplementary feeding in Australian cities [cf., @fuller2008garden].

@@

```{r Figure 1, echo=FALSE, fig.cap="An example of five different species' average radiance values."}
knitr::include_graphics("finalFigs/Figure1.pdf")
```

```{r Figure 2, echo=FALSE, fig.cap="The distribution, on a log-scale, of the response variable for the 477 species included in the analysis, with five example species highlighted."}
knitr::include_graphics("finalFigs/Figure2.pdf")
```

@@

```{r Figure S2, echo=FALSE, fig.cap="Phylogenetic uncertainty for some of the most important predictor variables included in the analysis."}
knitr::include_graphics("finalFigs/FigureS2.pdf")
```

>>>>

### Phylogenetic signal
There was a distinct phylogenetic signal in our urbanization index measure (Fig. 3; Fig. S2; Table 1), as it was significantly different than random for 4 out of the 5 indices considered. Additionally, there was strong phylogenetic signal for potential predictor traits, especially body size and brain residual (Table 1). The result for body size ($k=3.3$) is among the strongest ever recorded measures of phylogenetic signal in the literature, and for $k$ the statistic suggests much stronger signal than expected from Brownian motion. We generally found weaker signal for behavioral traits compared with morphological traits. For these traits, the estimates of phylogenetic signal were weaker than Brownian motion but significant in most cases (Table 1).

@@

# DISCUSSION
Niche breadth, as measured by different types of generalism, was significantly associated with urbanization in our analyses, evidenced by the robustness of this result across non-phylogenetic and phylogenetic models, model-averaging approaches, and across phylogenetic uncertainty (Fig. S3). Conversely, specialized feeding strategies were negatively associated with urbanization: granivorous and insectivorous specialists were much less likely to be found in urban environments. These results suggest that urbanization is, in general, excluding specialist species [@sorace2009distribution]. As such, future urban development aimed at increasing avian diversity in urban areas should focus on maintaining a high diversity of habitat [@melles2003urban] both for foraging [@shochat2004linking], and nesting [@fernandez2001habitat], with a focus on intact vegetation [@sushinsky2013should] connected by corridors [@litteral2017role]. A species-specific approach to assess particular resources necessary for specialist species may be necessary [@fernandez2004spatial]. Furthermore, a focal point of avian biodiversity conservation should be on increasing insect abundance and diversity in urban environments [@baldock2015uk], which will in turn benefit avian biodiversity in urban environments.

The non-random distribution of the urbanization index across the phylogeny (Table 1) is consistent with the observation of reduced phylogenetic diversity in urban areas [@la2018phylogenetic], suggesting that there are phylogenetic constraints which allow certain birds to persist within urban environments [@morelli2016evidence; @ibanez2017global; @sol2017urbanisation]. This finding of a strong phylogenetic signal contrasts with previous studies [@evans2011makes], but this is likely a result of increased statistical power from our larger sample size: 477 species in this study compared with 55 species in Evans *et al.* [-@evans2011makes]. It's not surprising that a larger sample size finds a non-random pattern in urbanization across the bird phylogeny and we demonstrated the importance of treating species as non-independent by considering phylogeny in the context of the linear models. For example, some predictor variables became less crucial in the phylogenetically controlled models compared with the non-phylogenetic models, including some feeding types (i.e., insect specialists) and habitat preferences (i.e., agricultural). For these variables, it is likely that there may be particular clades which include a number of species that are associated with both that particular trait and urbanization [see @felsenstein1985confidence]. Conversely, some of the most important predictor variables (e.g., clutch size and feeding habitat generalism; Figures 4 and 5) showed a stronger relationship (i.e., increased parameter estimates) with urbanization when phylogeny was accounted for, and this affect was robust relative to a consideration of phylogenetic uncertainty (Fig. S3). Furthermore, residual brain mass (and body size to a lesser extent) was significantly important within the phylogenetic models, but not in the non-phylogenetic models, suggesting that within a clade the species with the largest residual brain mass [@maklakov2011brains] and largest body size [@major2010museum] are most suited to surviving in urban areas. While some studies have found a lack of evidence that residual brain size is an important predictor in urban birds [@kark2007living; @evans2011makes], our results suggest that residual brain size is indeed heavily correlated with urbanization in birds [@moller2009successful; @maklakov2011brains; @moller2015brain]. This finding highlights the necessity to investigate the trait-urbanization relationships in a phylogenetically informed manner.

Certain aspects of the trait-urbanization relationship appear to be consistent, and thus generalizable, across the globe. For instance, our finding of the relative importance of annual fecundity is consistent with work in Europe [@croci2008does; @moller2009successful]. Urbanization appears to generally select against insectivorous species [@chace2006urban; @evans2011makes]. Although we did not find any strong support for our hypotheses on different nesting types, we did find that in general species which tended to be more social were closely associated with urbanization, consistent with other findings [@coleman1994neophobia; @jokimaki1998distribution; @kark2007living]. While these patterns may be generalizable, we also found patterns in our analysis which seem to contrast the global norm. For example, we found that urbanization selects against granivorous species, contrasting the general trend [@chace2006urban; @kark2007living; @evans2011makes], but this could be a result of relatively little supplementary feeding in Australian cities [cf., @fuller2008garden].

@@

```{r Figure 1, echo=FALSE, fig.cap="An example of five different species' average radiance value distributions, on a logarithmic scale."}
knitr::include_graphics("finalFigs/Figure1.pdf")
```

```{r Figure 2, echo=FALSE, fig.cap="The distribution, on a logarithmic scale, of the response variable for the 477 species included in the analysis, with five example species highlighted."}
knitr::include_graphics("finalFigs/Figure2.pdf")
```

@@

```{r Figure S2, echo=FALSE, fig.cap="A reference phylogenetic tree, with labeled tips, for each of the 477 species included in the analysis. Appendix 4 lists the 477 species."}
knitr::include_graphics("finalFigs/FigureS2.pdf")
```

```{r Figure S3, echo=FALSE, fig.cap="Phylogenetic uncertainty for some of the most important predictor variables included in the analysis."}
knitr::include_graphics("finalFigs/FigureS3.pdf")
```
